### 2010-01-21 trunk/deliverables/D2_4_Mediation/fast_d2_4_2_part1.tex
Added newest version of USGS article contents
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@442 d8b0c59b-6544-0410-94d9-83a5658a058e

@@

FAST uses ontology matching to conceptualise the underlying resources used by the different components.
Ontologies embody the fundamental vehicle for conceptualising data on semantic systems; they describe the context and semantic background of data that should be known to all agents using it. An ontology is used to define the vocabulary that agents use to exchange  queries and assertions. If an agent commits to a common ontology, it guarantees the consistency of the queries and assertions using the defined vocabulary \cite{gruber93towards}.
However, different ontologies are often used in the same scenario. This is also true for FAST, where gadget building blocks can originate from different providers, who might use different ontologies to describe them.  The task of ontology matching is therefore critical in FAST.

Given two ontologies $O$ and $O'$ that need to be mapped to each other, we adopt the definition given in \cite{shvaiko2005schema_based}: an ontology mapping element is a 5-tuple $<id, e, e', n, R>$, where 
%\begin{inparaenum}[(i)]
$id$ is a unique identifier, identifying the
mapping element, 
$e$ and $e'$ are entities (formulas, terms, classes, individuals) of the first and second ontology, respectively, 
$n$ is a confidence measure holding the correspondence value between $e$ and
$e'$, 
$R$ is the correspondence relation holding between $e$ and $e'$ (e.g., \texttt{equivalence (=)}, \texttt{more general($\sqsupseteq$)} or \texttt{disjointness($\perp$)}).
%; \texttt{overlapping($\sqcap$)}. 
%\end{inparaenum}
The alignment operation determines the mapping $M'$ for a pair of ontologies $O$ and $O'$. The alignment process can be extended by parameters, such as an input mapping, weights and thresholds and other external resources (dictionaries, thesauri, etc.). Different levels of mappings are defined:

A \textit{level 0} mapping~\cite{euzenat2004api} is a set of the above mapping elements, when the entities are discreet (defined by URIs). E.g., consider the ontology $O1$ with a class \texttt{Person}, and another ontology $O2$ with a class \texttt{Human}. For this case a matching algorithm  could return the mapping element $< id_{11}, Person, Human, 0.67, = >$, meaning that the \texttt{Person} class from the first ontology is found to be equivalent to the \texttt{Human} class in the second one with a confidence measure of \texttt{0.67}.

A \textit{level 1} mapping is a slight refinement of level 0, replacing pairs of elements with pairs of sets of elements.

A \textit{level 2} mapping can be more complex and defines correspondences in first order logic. It uses the ontology mapping language described in \cite{scharffe2005language}. It can describe complex correspondences, such as the one detailed in Section \ref{gr} for matching the Amazon and GoodRelations ontologies.
% :
% 
% \begin{equation*} \label{eq}
% \forall{x,z} grandparent(x,z) \Longrightarrow \exists{y}; parent(x,y) \wedge parent(y,z)
% \end{equation*}

@@

The gadget life cycle in FAST has several phases and roles associated, as detailed in \cite{hoyer-fast}. Here, we list the ones relevant for the ontology matching tasks, in decreasing order of the measure in which knowledge about ontologies is required.
\begin{inparaenum}[(i)]
    \item The \textit{ontology engineer} creates the ontologies used to annotate services and data. This role also includes the process of ontology matching, either automated or manually, determining if the alignment is feasible and creating so-called \emph{matching operator} building blocks, which are basic elements of the FAST screen building. We also mention the \textit{resource developer}, (who, in some cases, can be the same person as the one fulfilling the ontology engineer role), who uses these ontologies to annotate the the resources created in FAST.
    \item Ontology matching is needed by the \textit{screen developer} at the design-time of a screen (a visual building block of a gadget). Screen developers have a dedicated UI component for building screens, in which they can use the matching operators to combine components annotated with different ontologies. No actual matching is performed in this phase, but rather the simple possibility of matching.
%the FAST user interface determines if two resources can be combined or not (see Figure \ref{fig:screens} for a conceptual example of resources that can not be combined).
    \item The \emph{gadget developer} combines screens to screen-flows and gadgets, and only uses ontology matching implicitly.
    \item The \textit{end-user} uses the final deployed gadget, that combines the different services, but is unaware of the underlying resources and ontologies or the matching process. Thus we also need ontology matching at the gadget's run-time, where the mapping will have to be integrated into the actual JavaScript code of the running FAST gadget. %In this paper, we mainly consider the first two cases (i.e. ontology engineering and screen development), but portability of the alignment code to JavaScript must also be kept in mind.
\end{inparaenum}

@@

An ontology mapping (or alignment) is a declarative specification of the semantic overlap between two ontologies~\cite{debruin2005wsml}. It is the result of the ontology alignment process. This mapping is represented as a set of axioms in a mapping language. The mapping process has three main phases:
\begin{inparaenum}[(1)]
    \item discovering the mapping (alignment phase), 
    \item representing the mapping and 
    \item exploiting the mapping.
\end{inparaenum}

To accomplish this we need a tool to assist the ontology engineer in the ontology mapping process.
Based on the description given in Sect.~\ref{ominfast} we identify the following requirements for an alignment tool, that we will take as the basis for an ontology matching component in FAST:
\begin{inparaenum}[(i)]
\item All three phases of the process need to be accessible.
\item Matching of OWL and RDFS ontologies should be supported, since we only consider these two languages.
\item The tool should be as independent as possible, performing the alignment process with little or no user interference. This is an important requirement, since FAST is end-user oriented.
\item It should have an open source license, allowing its free use and modification, because it needs to be integrated into the free and open FAST platform.
\item The code should be suitable for porting to other languages (in particular JavaScript), allowing it to be integrated into the FAST environment.
\item It should be well documented.
\end{inparaenum}

We have considered three tools, two of which we have already detailed in \cite{ambrus2009mediation}.
\paragraph{MAFRA} \cite{maedche2002mafra} supports an interactive and incremental process of ontology mapping. It provides an explicit notion of semantic bridges. This representation is serialisable, portable and independent from the mapped languages. The bridges, however, have been designed to be used within the MAFRA system, and the alignment process needs to be done through the provided GUI.

\paragraph{RDFT}
\cite{omelayenko2002rdft} is a small language originally designed to map between XML and RDF. The results are mappings represented in DAML+OIL, that can be executed in a transformation process. No hints are given to add alignment methods or extending the format and, as a major downside, we have not been able to locate the tool for download and testing.

\paragraph{Alignment API} \cite{euzenat2004api} is the tool best matching the requirements, satisfying all the desired conditions. It also being widely used at the annual ontology matching evaluation campaigns and is under active development. It provides an API and its implementation, is open source (GPLv2 or above) and written in Java, providing an easy way to embed it into other programs. Alignment API can be extended by other representations and matching algorithms, it can be invoked through the command line interface (thus working without user interference) or one of the two available GUI implementations, or it can be exposed as an HTTP server. The tool allows for testing different alignment methods and can generate evaluation results based on a reference alignment. One of the major advantages is that it can generate the mapping result in XSLT, making it possible with the use of a simple tool, or a JavaScript package to transform XML data from one ontology into the other, independently from the alignment system.

@@

The scenario we want to test in FAST is taken from the e-commerce domain, based on the often-met case where a commercial agent aggregates data from other commercial websites. We consider the situation where a user needs a gadget which combines major e-commerce services, allowing to aggregate item lists from all of them in a combined interface.
As examples in our scenario. we consider the two most popular online shopping websites, Amazon and eBay\footnote{Based on the Alexa ranking from http://alexa.com/topsites/category/Top/Shopping}, along with BestBuy, which is very close behind the former two. BestBuy is an interesting case, because it exposes its data in RDF using the GoodRelations (GR) ontology~\cite{hepp-goodrelations}, which has recently gained a lot of popularity. It is therefore one of the first major e-commerce sites to provide semantic metadata.

\begin{figure}
    \centering
        \includegraphics[width=8cm]{images/screens_diagram.png}%[bb=0 0 201 126]
        \caption{The scenario: three components retrieving incompatible data}
    \label{fig:screens}
\end{figure}

Figure~\ref{fig:screens} illustrates our scenario. There are three retrieval components that wrap the different e-commerce sites and provide data according to three different ontologies: the GR ontology, the Amazon ontology and the eBay ontology. Another component displays GR items for display to the user. Out of the box, only the BestBuy retrieval and the display component can be combined. However, if the gadget designer wants to aggregate data from all three services in the display, there will have to be a mapping present between the Amazon and eBay on the one hand, and the GR ontology on the other.

@@

\subsection{Ontologies}
\label{ontologies}
We have used three ontologies to annotate underlying resources in FAST, the first of which, namely GoodRelations, is an extensive ontology for e-commerce. The other two, i.e., the Amazon and the eBay ontologies were developed by us as simplified versions of what would be used in the real-life scenarios. Nevertheless, they are sufficient for testing the feasibility of the scenario and the options presented by current ontology alignment methods.

\paragraph{GoodRelations:}
This ontology is aimed at annotating so-called ``offerings'' on the Web, which can be products or services. The ontology is  available under the Creative Commons Attribution 3.0 license and features support for ranges of units, measurements, currencies,  shipping and payments, common business functions (sell, lease, repair, etc.) and international standards (ISO 4217 or UNSPSC) and codes (e.g., EAN or UPC) in the field.

\begin{center}
\lstset{captionpos=b, breaklines=true}
\lstset{frame=single, basicstyle=\scriptsize}
\lstset{caption=Basic GoodRelations data in N3 notation, label=listing_gr}
\lstset{language=XML}
\begin{lstlisting}
:Offering_8794691     a gr:Offering;
  gr:hasPriceSpecification 
      :UnitPriceSpecification_8794691_1;
  gr:includesObject :TypeAndQuantityNode_8794691_1;

:UnitPriceSpecification_8794691_1     a gr:UnitPriceSpecification;
  gr:hasCurrency "USD"^^xsd:string;
  gr:hasCurrencyValue "749.99"^^xsd:float;
  gr:hasUnitOfMeasurement "C62"^^xsd:string;

:TypeAndQuantityNode_8794691_1     a gr:TypeAndQuantityNode;
  gr:amountOfThisGood "1.0"^^xsd:float;
  gr:hasUnitOfMeasurement "C62"^^xsd:string;
  gr:typeOfGood :ProductOrServicesSomeInstancesPlaceholder_8794691 .

:ProductOrServicesSomeInstancesPlaceholder_8794691 a gr:ProductOrServicesSomeInstancesPlaceholder;
  gr:hasEAN_UCC-13 "0013803096095"^^xsd:string;
  gr:hasMakeAndModel :PoSM_8794691;
  rdfs:comment "With Auto Optimization and [...]"@en;

:PoSM_8794691     a gr:ProductOrServiceModel;
  gr:hasManufacturer <bbuy:Manufacturer_Canon>;
  rdfs:label "Canon EOS Digital Rebel [...]"@en;
  rdfs:comment "With Auto Optimization and [...]"@en;
\end{lstlisting}
\end{center}

The ontology (see List.~\ref{listing_gr} for an example of GR data)  is centred on the \texttt{Offering} class,
which represents an announcement by a \texttt{BusinessEntity} to provide a \texttt{ProductOrService} with a given \texttt{BusinessFunction}. It may be constrained in terms of eligible business partner, countries, quantities, and other properties. It is also described by a given \texttt{PriceSpecification}. The super-class for all classes describing products or service types is \texttt{ProductOrService}. This top-level concept has sub-classes representing actual product instances, product models and dummy product placeholders. A product is described by its title and description, manufacturer, make and model, etc. While GoodRelations offers terminology to allow a much higher expressivity, we will restrict the discussion to those terms relevant for our scenario.

\paragraph{Amazon Ontology:}
We have created a small Amazon ontology based on the datatypes supported by the web service exposed by Amazon to third-party agents to use its services. It is a simplified version of what would be needed in a real-world application, but it suffices for the scope of this work. The ontology describes \texttt{Items} based on the \texttt{ItemAttributes} description given in the Amazon Product Advertising API documentation\footnote{http://docs.amazonwebservices.com/AWSECommerceService/latest/DG/}.

\begin{center}
\lstset{captionpos=b, breaklines=true}
\lstset{frame=single, basicstyle=\scriptsize}
\lstset{caption=Simplified Amazon ontology data in N3 notation, label=listing_amazon}
%\caption{Minimal Amazon ontology snippet.}
\lstset{language=XML}
%\lstset{emph={vsmlVariant, namespace, ontology, concept, ofType, instance, nonFunctionalProperties, endNonFunctionalProperties, memberOf, hasValue}}
%\lstset{emphstyle=\textbf\textit\underbar}
\begin{lstlisting}
:Item_7590645     a amzn:Item;
    amzn:hasASIN "B0012YA85A";
    amzn:hasManufacturer :Manufacturer_Canon;
    amzn:hasModel "XSI Kit";
    amzn:hasPrice :Price_7590645_1;
    amzn:hasProductGroup "Electronics";
    amzn:hasTitle "Canon Digital Rebel XSi [...]" .

:Manufacturer_Canon     a amzn:Company;
    amzn:hasLegalName "Canon" .

:Price_7590645_1     a amzn:ListPrice;
    amzn:hasAmount "575.55";
    amzn:hasCurrencyCode "GBP" .
\end{lstlisting}
\end{center}

The ontology features three classes for describing a product. Example instance data is given in List.~\ref{listing_amazon}.
\begin{inparaenum}[(1)]
    \item \texttt{Item} represents an Amazon item, defined by a title, a manufacturer, a product group (DVD, Book, etc.), an international EAN code, an ASIN (unique Amazon id), an author (for books) and a \texttt{ListPrice}. 
    \item \texttt{Company}, described by a  legal name, is used for representing the manufacturer of an \texttt{Item}.
    \item \texttt{ListPrice} has two properties: \texttt{hasCurrencyCode}, representing an ISO 4217 currency code (e.g. GBP or EUR), and \texttt{hasAmount} representing the price in the given currency.
\end{inparaenum}

\paragraph{eBay Ontology:}
The eBay ontology was created based on the eBay Shopping API \footnote{http://developer.ebay.com/DevZone/shopping/docs/CallRef/index.html} and is supposed to annotate data retrieved through the web service described by the given API. Like the Amazon ontology, it is a simplified case of what would be used in a real-world implementation.

\begin{center}
\lstset{captionpos=b, breaklines=true}
\lstset{frame=single, basicstyle=\small}
\lstset{caption=Simplified eBay ontology data in N3 notation, label=listing_ebay}
\lstset{language=XML}
\begin{lstlisting}

:SimpleItem_1320648     a ebay:SimpleItem;
  ebay:hasItemID "E012Y090912";
  ebay:hasBidCount :"4";
  ebay:hasCountry "UK";
  ebay:hasCurrentPrice :Price_1320648_1;
  ebay:hasPrimaryCategoryName "Electronics";
  ebay:hasTitle "Canon Digital Rebel XSi [...]" .
  ebay:hasDescription "Camera is practically unused. It's like new."

:Price_1320648_1     a ebay:CurrentPrice;
  ebay:hasAmount "575.55";
  ebay:hasAmountType "GBP" 
\end{lstlisting}
\end{center}

The ontology features three basic classes, (see Listing \ref{listing_ebay} for an example of ebay data)
\begin{inparaenum}[(1)]
    \item \texttt{SimpleItem} represents an eBay \texttt{Item}, that is sold by a \texttt{SimpleUser}. It is described by a title, a \texttt{CurrentPrice} (specifying the highest bid, or the selling price of fix-priced items), primary category name, manufacturer, model, EAN code, item ID (a unique eBay ID), bid count, end time of bid, country where the item is located, and a product ID (which supports major international product codes --- this property is from the Finding API).
    \item The \texttt{CurrentPrice} features a \texttt{hasAmountType} property, specifying the currency code, and a \texttt{hasAmount} property, which is the amount of money for a price per unit.
    \item \texttt{SimpleUser} contains information about eBay users. Users are described by a user ID, about me URL and the seller's positive feedback score. This class will not be used for capturing information on goods for our scenario, but is an essential component of the eBay system, which was the reason for its inclusion in the ontology.
\end{inparaenum}

@@

There is a major paradigm difference between the GoodRelations ontology and the other two ontologies (see Sect.~\ref{results} for details). After studying the approach of the GR ontology, and examining the matching results between the Amazon and GR ontologies, we have concluded that automated matching between the two is unfeasible using the string-based methods employed using the Alignment API tool in this testing. Therefore, we have have created a manual mapping for this case, and have tested the automated matching on the Amazon--eBay pair, which closely resemble each other in their approach to capturing product details.

\subsubsection{The Matcher}
The matching tool called Alignment API \cite{euzenat2004api} has been developed to support several kinds of algorithms and methods, and provide an efficient environment for testing alignment systems.

\paragraph{The Algorithm:}
We have used a simple string distance-based algorithm provided by the tool, which computes the string distance between the names of the entities to find correspondences between them. Four methods have been used for computing the distance:
\begin{inparaenum}[(1)]
    \item equality, which tests whether the names are identical, 
    \item Levenshtein distance (number of character operations needed), 
    \item SMOA distance (which is a specialised distance for matching ontology identifiers) and
    \item a Wordnet-based~\cite{fellbaum1998wordnet} distance using the JWNL library with Wordnet.
\end{inparaenum}

\paragraph{The Alignment Description:} 
The alignment description is given based on a simple vocabulary, containing a pair of ontologies and a set of correspondences, which express relations holding among entities of the two ontologies.

We used the level 0 mapping representation for representing simple mappings, which map discrete entities of the two ontologies. Thus the representation of the correspondences is given with the five elements described (with the \texttt{id} being optional), as shown in List.~\ref{listing_correspondence}. Level 2 mappings were also used for more complex, manually-created representations, as detailed in Sect.~\ref{results}.

\begin{center}
\lstset{frame=single, basicstyle=\small}
\lstset{caption=Level 0 mapping element example, label=listing_correspondence}
\lstset{captionpos=b}
\lstset{language=XML}
%\lstset{emph={vsmlVariant, namespace, ontology, concept, ofType, instance, onFunctionalProperties, endNonFunctionalProperties, memberOf, hasValue}}
%\lstset{emphstyle=\textbf\textit\underbar}
\begin{lstlisting}
[ a :Cell;
  :entity1 amzn:hasCurrencyCode;
  :entity2 ebay:hasAmountType;
  :measure "1.0"^^xsd:float;
  :relation "=" ]
\end{lstlisting}
\end{center}

\paragraph{Using the Tool:}
The Alignment API tool can be used through a GUI, as a server or from the command-line interface, of which we have chosen the last one. The tool reads two RDF/OWL ontologies, computes the alignment between them, performs some thresholding and displays the results. It can render the output in a number of formats, including HTML and XSLT.

>>>>

\lstset{
captionpos=b, 
extendedchars=true,
basicstyle=\scriptsize \sffamily, 
stringstyle=\bfseries,
frame=single,
frameround=tttt,
showstringspaces=false,
breaklines=true,
}

\lstdefinelanguage{turtle} 
{morekeywords={@prefix, a}, 
sensitive=false, 
morecomment=[l]{\#}, 
morestring=[b]",
}

@@

FAST uses ontologies to conceptualise the underlying resources used by the different components.
Ontologies embody the fundamental vehicle for conceptualising data on semantic systems; they describe the context and semantic background of data that should be known to all agents using it~\cite{gruber93towards}.
However, different ontologies are often used to describe the same domain or cover the same scenario. This is also true for FAST, where gadget building blocks can originate from different providers, who might use different ontologies to describe them. To ensure interoperability, the task of ontology matching is therefore critical in FAST.

Given two ontologies $O$ and $O'$ that need to be mapped to each other, we adopt the definition given in~\cite{shvaiko2005schema_based}: an ontology mapping element is a 5-tuple $<id, e, e', n, R>$, where 
%\begin{inparaenum}[(i)]
$id$ is a unique identifier, identifying the
mapping element, 
$e$ and $e'$ are entities (formulas, terms, classes, individuals) of the first and second ontology, respectively, 
$n$ is a confidence measure holding the correspondence value between $e$ and
$e'$, 
$R$ is the correspondence relation holding between $e$ and $e'$ (e.g., \texttt{equivalence (=)}, \texttt{more general($\sqsupseteq$)} or \texttt{disjointness($\perp$)}).
%; \texttt{overlapping($\sqcap$)}. 
%\end{inparaenum}
The alignment operation determines the mapping $M'$ for a pair of ontologies $O$ and $O'$. The alignment process can be extended by parameters, such as an input mapping, weights and thresholds and other external resources (dictionaries, thesauri, etc.). Different levels of mappings are defined:

\begin{inparaenum}[(a)]
    \item A \textit{level 0} mapping~\cite{euzenat2004api} is a set of the above mapping elements, when the entities are discreet (defined by URIs). E.g., consider the ontology $O1$ with a class \texttt{Person}, and another ontology $O2$ with a class \texttt{Human}. For this case a matching algorithm  could return the mapping element $< id_{11}, Person, Human, 0.67, = >$, meaning that the \texttt{Person} class from the first ontology is found to be equivalent to the \texttt{Human} class in the second one with a confidence measure of \texttt{0.67}.
    \item A \textit{level 1} mapping is a slight refinement of level 0, replacing pairs of elements with pairs of sets of elements.
    \item A \textit{level 2} mapping can be more complex and defines correspondences in first order logic. It uses the ontology mapping language described in~\cite{scharffe2005language}. It can describe complex correspondences, such as the one detailed in Section \ref{sub:manual_mapping}.
\end{inparaenum}
% :
% 
% \begin{equation*} \label{eq}
% \forall{x,z} grandparent(x,z) \Longrightarrow \exists{y}; parent(x,y) \wedge parent(y,z)
% \end{equation*}

@@

The gadget life cycle in FAST has several phases and roles associated, as detailed in \cite{hoyer-fast}. Here, we list the ones relevant for the ontology matching tasks, in decreasing order of the measure in which knowledge about ontologies is required. Note that several roles can be played by the same actor.
\begin{inparaenum}[(i)]
    \item The \textit{ontology engineer} creates the ontologies used to annotate services and data. This role also includes the process of ontology matching, either automated or manually, determining if the alignment is feasible and creating so-called \emph{matching operator} building blocks, which are basic elements of the FAST screen building. The \textit{resource developer} then uses these ontologies to annotate resources created in FAST.
    \item Ontology matching is needed by the \textit{screen developer} at the design-time of a screen (a visual building block of a gadget). Screen developers have a dedicated UI component for building screens, in which they can use the matching operators to combine components annotated with different ontologies. No actual matching needs to be performed in this phase, but rather the possibility of matching needs to be determined (i.e., \emph{can} two screens A and B be combined?).
%the FAST user interface determines if two resources can be combined or not (see Figure \ref{fig:screens} for a conceptual example of resources that can not be combined).
    \item The \emph{gadget developer} combines screens to screen-flows and gadgets, and only uses ontology matching implicitly.
    \item The \textit{end-user} uses the final deployed gadget at run-time, but is unaware of the underlying resources and ontologies or the matching process. Only at run-time the actual mapping of instance data has to be performed. In this paper, we mainly consider the first two cases (i.e. ontology engineering and screen development).
\end{inparaenum}

@@

An \emph{ontology mapping} is a declarative specification of the semantic overlap between two ontologies~\cite{debruin2005wsml}. It is the result of the \emph{ontology alignment process}. This mapping is represented as a set of axioms in a \emph{mapping language}. The mapping process has three main phases:
\begin{inparaenum}[(1)]
    \item discovering the mapping (alignment phase), 
    \item representing the mapping and 
    \item exploiting the mapping.
\end{inparaenum}

To accomplish this we need a tool to assist the ontology engineer in the ontology mapping process.
Based on the description given in Sect.~\ref{ominfast} we identify the following requirements for an alignment tool, that we will take as the basis for an ontology matching component in FAST:
\begin{inparaenum}[(i)]
\item All three phases of the process need to be accessible.
\item Matching of OWL and RDFS ontologies must be supported in the FAST project.
\item The tool should be as independent as possible, performing the alignment process with little or no user interference. This is an important requirement, since FAST is end-user oriented.
\item The tool needs to be open source, allowing it to be integrated into the free and open FAST platform.
\item The code should be suitable for porting to other languages (in particular JavaScript), allowing it to be integrated into the FAST gadget run-time.
\item It should be well documented.
\end{inparaenum}

Based on these requirements, we compared three different tools. \emph{MAFRA}~\cite{maedche2002mafra} supports an interactive and incremental process of ontology mapping. It provides an explicit notion of semantic bridges. This representation is serialisable, portable and independent from the mapped languages. The bridges, however, have been designed to be used within the MAFRA system, and the alignment process needs to be done through the provided GUI. \emph{RDFT}~\cite{omelayenko2002rdft} is a small language originally designed to map between XML and RDF. The results are mappings represented in DAML+OIL, that can be executed in a transformation process. No hints are given to add alignment methods or extending the format and the tool does not longer seem to be available. \emph{Alignment API}~\cite{euzenat2004api} is the tool best matching our requirements, satisfying all the desired conditions. It is still under active development, provides an API and its implementation, is open source (GPLv2 or above) and written in Java, providing an easy way to embed it into other programs. Alignment API can be extended by other representations and matching algorithms, it can be invoked through the command line interface (thus working without user interference) or one of the two available GUI implementations, or it can be exposed as an HTTP server. The tool allows for testing different alignment methods and can generate evaluation results based on a reference alignment. Alignment API can generate the mapping results in XSLT, therefore providing an easy way to integrate them into other systems.

@@

In our evaluation scenario, which is taken from the e-commerce domain, a user needs to build a gadget which combines data from major e-commerce services, allowing to aggregate item lists from all of them in a combined interface.
As examples in our scenario, we consider the two most popular online shopping websites\footnote{\url{http://alexa.com/topsites/category/Top/Shopping}, checked 01/11/2009}, Amazon and eBay, along with the BestBuy site. The latter is an interesting case, because it exposes its data in RDF using the GoodRelations (GR) ontology~\cite{hepp-goodrelations}, which has recently gained a lot of popularity. It is therefore one of the first major e-commerce sites to provide semantic metadata.

\begin{figure}
    \centering
        \includegraphics[width=8cm]{images/screens_diagram.png}%[bb=0 0 201 126]
        \caption{Three gadget components retrieving incompatible data}
    \label{fig:screens}
\end{figure}

Figure~\ref{fig:screens} illustrates our scenario. There are three retrieval components that wrap the different e-commerce sites and provide data according to three different ontologies: the GR ontology, the Amazon ontology (A) and the eBay ontology (E). Another component displays GR items for display to the user, but not A or E items. If the gadget designer wants to aggregate data from all three services in the display, there will therefore have to be a mapping present between A and E on the one hand, and GR on the other.

@@

\subsection{Ontologies}
\label{ontologies}
Of the three ontologies used in our evaluation, only GoodRelations is a real-world, extensive ontology for e-commerce. The other two, i.e., the Amazon and the eBay ontologies were developed for simulation purposes as simplified versions of what would be used in the real-life scenarios. They were designed to showcase particular features of ontology mapping in our scenario.

\paragraph{GoodRelations:}
This ontology is aimed at annotating so-called ``offerings'' on the Web, which can be products or services. The ontology features support for ranges of units, measurements, currencies,  shipping and payments, common business functions (sell, lease, repair, etc.) and international standards (ISO 4217 or UNSPSC) and codes (e.g., EAN or UPC) in the field.
The main class is \texttt{Offering},
which represents an announcement by a \texttt{BusinessEntity} to provide a \texttt{ProductOrService} with a given \texttt{BusinessFunction}. It may be constrained in terms of eligible business partner, countries, quantities, and other properties. It is also described by a given \texttt{PriceSpecification}. The super-class for all classes describing products or service types is \texttt{ProductOrService}. This top-level concept has sub-classes representing actual product instances, product models and dummy product placeholders. A product is described by its title and description, manufacturer, make and model, etc. 
% While GoodRelations offers terminology to allow a much higher expressivity, we will restrict the discussion to those terms relevant for our scenario.

% \begin{center}
% \lstset{captionpos=b, breaklines=true}
% \lstset{frame=single, basicstyle=\scriptsize}
% \lstset{caption=Basic GoodRelations data in N3 notation, label=listing_gr}
% \lstset{language=XML}
% \begin{lstlisting}
% :Offering_8794691     a gr:Offering;
%   gr:hasPriceSpecification 
%       :UnitPriceSpecification_8794691_1;
%   gr:includesObject :TypeAndQuantityNode_8794691_1;
% 
% :UnitPriceSpecification_8794691_1     a gr:UnitPriceSpecification;
%   gr:hasCurrency "USD"^^xsd:string;
%   gr:hasCurrencyValue "749.99"^^xsd:float;
%   gr:hasUnitOfMeasurement "C62"^^xsd:string;
% 
% :TypeAndQuantityNode_8794691_1     a gr:TypeAndQuantityNode;
%   gr:amountOfThisGood "1.0"^^xsd:float;
%   gr:hasUnitOfMeasurement "C62"^^xsd:string;
%   gr:typeOfGood :ProductOrServicesSomeInstancesPlaceholder_8794691 .
% 
% :ProductOrServicesSomeInstancesPlaceholder_8794691 a gr:ProductOrServicesSomeInstancesPlaceholder;
%   gr:hasEAN_UCC-13 "0013803096095"^^xsd:string;
%   gr:hasMakeAndModel :PoSM_8794691;
%   rdfs:comment "With Auto Optimization and [...]"@en;
% 
% :PoSM_8794691     a gr:ProductOrServiceModel;
%   gr:hasManufacturer <bbuy:Manufacturer_Canon>;
%   rdfs:label "Canon EOS Digital Rebel [...]"@en;
%   rdfs:comment "With Auto Optimization and [...]"@en;
% \end{lstlisting}
% \end{center}

\paragraph{Amazon Ontology:}
We have created a small Amazon ontology based on a subset of the datatypes supported by the web service exposed by Amazon to third-party agents. The ontology describes \texttt{Items} based on the \texttt{ItemAttributes} description given in the Amazon Product Advertising API documentation\footnote{\url{http://docs.amazonwebservices.com/AWSECommerceService/latest/DG/}}.
The ontology features three classes for describing a product. Example instance data is given in List.~\ref{listing_amazon}.
\begin{inparaenum}[(1)]
    \item \texttt{Item} represents an Amazon item, defined by a title, a manufacturer, a product group (DVD, Book, etc.), an international EAN code, an ASIN (unique Amazon id), an author (for books) and a \texttt{ListPrice}. 
    \item \texttt{Company}, described by a  legal name, is used for representing the manufacturer of an \texttt{Item}.
    \item \texttt{ListPrice} has two properties: \texttt{hasCurrencyCode}, representing an ISO 4217 currency code (e.g. GBP or EUR), and \texttt{hasAmount} representing the price in the given currency.
\end{inparaenum}

% \begin{figure}[ht]
\lstset{caption=Simplified Amazon ontology data in N3 notation, label=listing_amazon}
\lstset{language=turtle}
\begin{lstlisting}
:Item_7590645 a amzn:Item;
   amzn:hasASIN "B0012YA85A";
   amzn:hasManufacturer :Manufacturer_Canon;
   amzn:hasModel "XSI Kit";
   amzn:hasPrice :Price_7590645_1;
   amzn:hasProductGroup "Electronics";
   amzn:hasTitle "Canon Digital Rebel XSi [...]" .
:Manufacturer_Canon a amzn:Company;
   amzn:hasLegalName "Canon" .
:Price_7590645_1 a amzn:ListPrice;
   amzn:hasAmount "575.55";
   amzn:hasCurrencyCode "GBP" .
\end{lstlisting}
% \end{figure}

\paragraph{eBay Ontology:}
The eBay ontology was created based on the eBay Shopping API\footnote{\url{http://developer.ebay.com/DevZone/shopping/docs/CallRef/index.html}} and is supposed to annotate data retrieved through the web service described by the API.
% \begin{center}
% \lstset{captionpos=b, breaklines=true}
% \lstset{frame=single, basicstyle=\small}
% \lstset{caption=Simplified eBay ontology data in N3 notation, label=listing_ebay}
% \lstset{language=XML}
% \begin{lstlisting}
% 
% :SimpleItem_1320648     a ebay:SimpleItem;
%   ebay:hasItemID "E012Y090912";
%   ebay:hasBidCount :"4";
%   ebay:hasCountry "UK";
%   ebay:hasCurrentPrice :Price_1320648_1;
%   ebay:hasPrimaryCategoryName "Electronics";
%   ebay:hasTitle "Canon Digital Rebel XSi [...]" .
%   ebay:hasDescription "Camera is practically unused. It's like new."
% 
% :Price_1320648_1     a ebay:CurrentPrice;
%   ebay:hasAmount "575.55";
%   ebay:hasAmountType "GBP" 
% \end{lstlisting}
% \end{center}
The ontology features three basic classes,
%  (see Listing \ref{listing_ebay} for an example of ebay data)
\begin{inparaenum}[(1)]
    \item \texttt{SimpleItem} represents an eBay \texttt{Item}, that is sold by a \texttt{SimpleUser}. It is described by a title, a \texttt{CurrentPrice} (specifying the highest bid, or the selling price of fix-priced items), primary category name, manufacturer, model, EAN code, item ID (a unique eBay ID), bid count, end time of bid, country where the item is located, and a product ID (which supports major international product codes --- this property is from the Finding API).
    \item The \texttt{CurrentPrice} features a \texttt{hasAmountType} property, specifying the currency code, and a \texttt{hasAmount} property, which is the amount of money for a price per unit.
    \item \texttt{SimpleUser} contains information about eBay users. Users are described by a user ID, about me URL and the seller's positive feedback score. This class will not be used for capturing information on goods for our scenario, but is an essential component of the eBay system, which was the reason for its inclusion in the ontology.
\end{inparaenum}

@@

There is a major paradigm difference between the GoodRelations ontology and the other two ontologies (see Sect.~\ref{sub:manual_mapping} for details). After some initial testing, we concluded that automatic mapping from GR to A/E using the string-based methods employed by the Alignment API tool was not feasible. Therefore, the following sections report on \emph{automatic mapping} for the A--E pair --- which are similar enough to be suitable for level 0 mapping ---, and \emph{manual mapping} for the GR--A/E pairs.

\subsubsection{Automatic Mapping}

% \paragraph{The Matcher} % (fold)
% \label{par:the_matcher}

% paragraph the_matcher (end)
For automatic mapping of level 0 mappings, we used a simple string distance-based algorithm provided by Alignment API~\cite{euzenat2004api}, which computes the string distance between the names of the entities to find correspondences between them. Four methods have been used for computing the distance:
\begin{inparaenum}[(1)]
    \item equality, which tests whether the names are identical, 
    \item Levenshtein distance (number of character operations needed), 
    \item SMOA distance (which is a specialised distance for matching ontology identifiers) and
    \item a Wordnet-based~\cite{fellbaum1998wordnet} distance using the JWNL library with Wordnet.
\end{inparaenum}

The alignment description derived from these methods is given based on a simple vocabulary, containing a pair of ontologies and a set of correspondences, which express relations between entities of the two ontologies.
We used the level 0 mapping representation for representing simple mappings, which map discrete entities of the two ontologies. Thus the representation of the correspondences is given with the five elements described (with the \texttt{id} being optional), as shown in List.~\ref{listing_correspondence}. Similar mappings were were also used for more complex, manually-created representations (level 2), as detailed in Sect.~\ref{sub:manual_mapping}.

% \begin{figure}[ht]
% \begin{minipage}{\linewidth}
\lstset{caption=Level 0 mapping element example, label=listing_correspondence}
\lstset{language=turtle}
\begin{lstlisting}
<level_0_mapping> a align:Cell;
  align:entity1 amzn:hasCurrencyCode;
  align:entity2 ebay:hasAmountType;
  align:measure "1.0"^^xsd:float;
  align:relation "=" .
\end{lstlisting}
% \end{minipage}
% \end{figure}

% \subsubsection{Using the Tool.}
% The Alignment API tool can be used through a GUI, as a server or from the
% command-line interface, of which we have chosen the last one.
% The tool reads two RDF/OWL ontologies, computes the alignment between them, 
% performs some thresholding and displays the results. It can render the output
% in a number of formats, including HTML and XSLT.
% 
% An additional feature of the tool is its ability to evaluate results based on
% a reference alignment, and output the evaluation results in a table,
% or plot them as \LaTeX{} graphs.
